---
title: "TMT Pipeline Package Benchmark"
output: html_document
date: "2022-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TMTPipeline)
library(PNNL.DMS.utils)
library(PlexedPiper)
library(MSnID)
library(DT)
library(data.table)
library(dplyr)
```

## Summary

The goal of this markdown is to show Lisa and Paul the results for the pipeline 
to process MASIC (abundances) and MS-GF+ (peptide/protein identification) data to pmartR
data objects, and help them make educated choices regarding each step. 

The pipeline is relatively simple: 

0. Pull MS-GF+ and MASIC results from DMS. This is done externally to this package with PNNL.DMS.UTIL. It will eventually be replaced. 

1. Filter MS-GF+ data
    a. Filter to a FDR > 0.01 and MS1 PPM error > 10. We use the MSnID package.
    b. Then remove decoys 
    
2. Filter MASIC Data 
    a. Filter out interference scores of less than 0.5 
    
3. Combine and generate pmartR objects 

Note that in step 1, it is essential that decoys are filtered after the FDR 
filtering step.

## Data Package 4005

Load data objects: 

```{r}
# Load files
res <- readRDS("C:/Users/degn400/OneDrive - PNNL/Desktop/OldProjects/TMT/4005_Tafess_LI/4005_Data_Package.RDS")
job_records <- res$job_records
msnid <- res$msnid
masic_data <- res$masic_data
metadata <- xlsx::read.xlsx("/Users/degn400/OneDrive - PNNL/Desktop/OldProjects/TMT/4005_Tafess_LI/Tafess_LI_metadata.xlsx", 1)
```

#### Filter FDR > 0.01 and PPM Error > 10

**Old pipeline:** 

```{r}
msnid_FDR_old <- filter_msgf_data(msnid, level="peptide", fdr.max=0.01)
msnid_FDR_old
```

**New pipeline**

```{r}
msnid_FDR_new <- fdr_filter(msnid)
msnid_FDR_new
```

#### Filter Decoys 

**Old pipeline:**

```{r}
msnid_decoy_old <- apply_filter(msnid_FDR_old, "!isDecoy")
msnid_decoy_old
```

**New pipeline:**

```{r}
msnid_decoy_new <- decoy_filter(msnid_FDR_new)
msnid_decoy_new
```

#### Filter Interference > 0.5

**Old pipeline:**

```{r}
masic_filtered_old <- filter_masic_data(masic_data,
                                        interference_score_threshold = 0.5,
                                        s2n_threshold = 0)
nrow(masic_filtered_old)
```

**New pipeline:**

```{r}
class(masic_data) <- c(class(masic_data), "masic_data")
masic_filtered_new <- interference_filter(masic_data, remove_all_missing = FALSE)
nrow(masic_filtered_new)
```

#### Create CrossTabs 

**Old pipeline:**

```{r}
fractions <- 

crosstab <- create_crosstab(msnid_decoy_old, masic_filtered_old,
                            aggregation_level = "peptide",
                            fractions, samples, references)

```


